---
layout: post
title: "Test Markdown Document"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path="../images/")
```

## GitHub Documents

This is a test post for me to remember what I did originally. I used Andy South's terrific blog as a guide: http://andysouth.github.io/blog-setup/. Most of this .Rmd file was created by RStudio when I created a new R Markdown file using the predefined GitHub format.

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

I created a folder called _rmd in the root directory to where I move this .Rmd file. The reason for this is that _posts will contain a .md and a .Rmd file, but the .Rmd file is not well read by GitHub pages. I also added the option fig.path="../images/" to opt_chunk$set() above. This places all my plots in the images folder in the root directory, as seen by the pressure plot below.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r chunk13-12-2016-pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
